New lower bounds for Schur and weak Schur numbers

### 2021-04-07 article/weakschur.tex
Update weakschur.tex
ajout WE+

>>>>

\begin{remark}
This formula includes the results of Rowley \hyperlink{label2}{\textbf{[2]}} as a special case. For \(n>2\), this formula does not give new lower bounds but in the same way as we introduced \(SE_+\)\hyperref[SE]{(Definition 3.1)}, we will define \(WE_+\) and find inequalities between \(WE_+\),\(WS\) and \(S\)
\end{remark}

\subsection{Definition of \(WE_+\)}

\begin{definition}
Let \( n \in \mathbb{N}^*\), let\( b \in \mathbb{N}^*\) there exists a greatest integer that we note \(WE_b^+(n)\) such that \( [\![1, b+WE_b^+(n)]\!]\) can be partitionned into \(n\) weakly-sum-free subsets \(A_1, A_2, ..., A_n\) which verify :
\\\\
\underline{\(\forall i \in [\![1, n]\!], \quad A_i\backslash [\![1, b]\!]\) is sum-free}
\\\\
\underline{For \(A_n\) (the special subset):} \quad \(\forall (x,y) \in A_n^2,\)
\\
\[if \quad x+y>b+2WE_b^+(n),\quad x+y-2WE_b^+(n)\notin A_n\]
\\
\underline{For the others subsets:}\quad \(\forall (x,y) \in A_k^2\)
\\
\[
(Id+WE_b^+(n)\mathbf{1}_{ [\![0,b]\!]})(x+y[WE_b^+(n)]) \notin A_k
\]

\end{definition}

\begin{Theorem}
Let \( n \in \mathbb{N}^*\), let\( (a,b) \in (\mathbb{N}^*)^2\) such as \(a>b\). If there exist a partition of  
\end{Theorem}
